Efficient Shapelet Computation for Silhouette Score

### 2024-03-01 main.tex
minor change

\section{Related Work}
NN-Descent~\cite{NN-Descent} is based on the principle: \textit{A neighbor of
a neighbor is likely to be a neighbor}. The idea is, given an approximation of 
the nearest neighbor, then the approximation can be improved by exploring the 
neighbors of the neighbors of each point. To improve the running time, the 
authors use local join to avoid comparing same points many times in the same 
iteration. They also use incremental search to avoid comparing points that have
been compared in previous iterations. Also, sampled is used to lower the 
overhead of local joins. Finally, random projection trees are used to 
initialize the graph.

>>>>

\section{Related Work}
NN-Descent~\cite{NN-Descent} is based on the principle: \textit{A neighbor of
a neighbor is likely to be a neighbor}. The idea is, given an approximation 
graph of the nearest neighbor, then the approximation can be improved, 
in an iterative fashion, by exploring the neighbors of the neighbors of each 
point. To improve the running time, the authors use local join to avoid 
comparing same points many times in the same iteration. They also use 
incremental search to avoid comparing points that have been compared in 
previous iterations. Also, sampled is used to lower the overhead of local 
joins. Finally, random projection trees are used to initialize the graph.
